### 2022-02-19 extension.rmd
Add small fixes to the mentions of online appendix

---
title             : "Appendix to \"Bayesian (comparative) journalism studies\""
shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"

@@

Another way to compare the cubic model and the parsimonious model is to conduct a leave-one-out cross validation (LOO). The basic idea of LOO is to study the out-of-sample accuracy of the model by removing one data point at a time. Given the rest of the data and the prediction model, we evaluate how accurate is the model to predict the outcome of the removed data point. The Bayesian LOO estimate of out-of-sample predictive fit ($elpd_{loo}$) can used to compare the out-of-sample accuracy of models [@vehtari:2016:PBW].

@@

The difference in $elpd_{loo}$ between the cubic model and the parsimonious model is only -0.3 but with a standard error of 0.5. One would say there is a difference in out of sample model fit, when $elpa_{loo}$ is many times larger than its standard error.

>>>>

---
title             : "Online appendix to \"Bayesian (comparative) journalism studies\""
shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"

@@

Another way to compare the cubic model and the parsimonious model is to conduct a leave-one-out cross validation (LOO). The basic idea of LOO is to study the out-of-sample accuracy of the model by removing one data point at a time. Given the rest of the data and the prediction model, one evaluates how accurate is the model to predict the outcome of the removed data point. The Bayesian LOO estimate of out-of-sample predictive fit ($elpd_{loo}$) can be used to compare the out-of-sample accuracy of models [@vehtari:2016:PBW].

@@

The difference in $elpd_{loo}$ between the cubic model and the parsimonious model is only -0.3 with a larger standard error of 0.5. One would say there is a difference in out of sample model fit, when $elpa_{loo}$ is many times larger than its standard error.

### 2022-02-19 manuscript.rmd
Add small fixes to the mentions of online appendix

[^dict_val]: The validation of the dictionary is available in the Appendix.

@@

We propose four extensions to the above barebone analysis: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes. The analyses in these extensions are not preregistered. Please refer to Appendix I for these extensions.

@@

[^loo]: Another way to evaluate the model fit is to use leave-one-out cross validation. See Appendix for the analysis.

>>>>

[^dict_val]: The validation of the dictionary is available in the online appendix.

@@

We propose four extensions to the above barebone analysis: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes. The analyses in these extensions are not preregistered. Please refer to the online appendix for these extensions.

@@

[^loo]: Another way to evaluate the model fit is to use leave-one-out cross validation. See the online appendix for the analysis.
